|

### 2023-02-08 paper.tex
Wed Feb  8 19:08:36 CET 2023: update-remote.sh

The DAE-GP algorithm, first described by {[}\protect\hyperlink{ref-dae-gp_2020_rtree}{33}{]}, is summarized as a flowchart in figure \ref{fig:daegp-flowchart}.
After setting the generation counter \(g\) to \(0\) and creating the initial population of solutions \(P_0\), DAE-GP enters the main loop that checks if a termination criteria is satisfied (i.e.~maximum number of generations or fitness evaluations is reached).
For each generation \(g\) the fitness of all new individuals in \(P_g\) is evaluated. During model building, DAE-GP selects a subset \(X_g\) of the current population that is used as training data for the DAE-LSTM model \(M_g\) which is trained to learn the properties of \(X_g\).
The trained model \(M_g\) is then used for model sampling, partially mutated solutions from \(P_G\) are propagated through \(M_g\) to create a new population \(P_{g+1}\).
This process is repeated until the termination criteria is met and DAE-GP returns the highest fitness solutions.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model \(M_G\), we see one main reason for the large run-time increase by pre-training DAE-GP. Figure \ref{fig:airfoil-SamplingTime} shows the median sampling time spend during each generation of the search and it clearly demonstrates that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP. The median time spend on sampling new individual for regular DAE-GP increases by a factor of 6.83 from 29.05581 seconds to 198.4503 seconds.

@@

\ldots hier einfügen\ldots{}

>>>>

The DAE-GP algorithm, first described by {[}\protect\hyperlink{ref-dae-gp_2020_rtree}{33}{]}, is summarized as a flowchart in figure \ref{fig:daegp-flowchart}.
After setting the generation counter \(g\) to \(0\) and creating the initial population of solutions \(P_0\), DAE-GP enters the main loop that checks if a termination criteria is satisfied (i.e.~maximum number of generations or fitness evaluations is reached).
For each generation \(g\) the fitness of all new individuals in \(P_g\) is evaluated. During model building, DAE-GP selects a subset \(X_g\) of the current population that is used as training data for the DAE-LSTM model \(M_g\) which is trained to learn the properties of \(X_g\).
The trained model \(M_g\) is then used for model sampling, partially mutated solutions from \(P_g\) are propagated through \(M_g\) to create a new population \(P_{g+1}\).
This process is repeated until the termination criteria is met and DAE-GP returns the highest fitness solutions.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model \(M_g\), we see one main reason for the large run-time increase by pre-training DAE-GP. Figure \ref{fig:airfoil-SamplingTime} shows the median sampling time spend during each generation of the search and it clearly demonstrates that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP. The median time spend on sampling new individual for regular DAE-GP increases by a factor of 6.83 from 29.05581 seconds to 198.4503 seconds.

@@

\begin{center}\includegraphics{private/statutory_declaration} \end{center}
